jk test with unbalanced label

### 2016-10-04 Rmd/convergenceRatesImbalanced.Rmd
update labeling issue

---
title: "jk test with balanced label"
author: "Author"
date: '`r Sys.Date()`'
output:
  md_document: 
    variant: markdown_github
---

@@

###1. Generate Data
Let's generate data from 2 clusters, with size n, n

N( c(0.7), diag(1.7661/30))
N( c(0.3), diag(1.7661/30))

@@

mu0<- c(c(0.3), c(0.7))
mu<- matrix( 0,n*2,p)
mu[1:(n),]<- rep(c(0.3),each=(n))
mu[(n+1):(2*n),]<- rep(c(0.7),each=(n))

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}
computeMError<- function(jk, n,batchN){
  error<- numeric(batchN)
  for(b in 1:batchN){
    tM0<- rank(jk$mu[,1,b])-1
    trueM<- rep(tM0,each=n)
    error[b]<- sum ( jk$M[,b] != trueM) /K/n
    if( min(jk$w[,b])<0.1){
        error[b]<- NA
    }
  }
  error
}

@@

  save(result, file="resultRatesBalanced.Rda")
}

@@

load("resultRatesBalanced.Rda")

>>>>

---
title: "jk test with unbalanced label"
author: "Author"
date: '`r Sys.Date()`'
output:
  md_document: 
    variant: markdown_github
---

@@

###1. Generate Data
Let's generate data from 2 clusters, with size n/2, n/2*3

N( c(0.3), diag(1.7661/30))
N( c(0.7), diag(1.7661/30))

@@

mu0<- c(c(0.3), c(0.7))
mu<- matrix( 0,n*2,p)
mu[1:(n/2),]<- rep(c(0.3),each=(n/2))
mu[(n/2+1):(2*n),]<- rep(c(0.7),each=(n/2*3))

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}

computeMError<- function(jk, n,batchN){
  error<- numeric(batchN)
  for(b in 1:batchN){
    tM0<- rank(jk$mu[,1,b])-1
    trueM<- c(rep(tM0[1],(n/2)),rep(tM0[2],(n/2*3)))
    error[b]<- sum ( jk$M[,b] != trueM) /K/n
    if( min(jk$w[,b])<0.1){
        error[b]<- NA
    }
  }
  error
}

@@

  save(result, file="resultRatesImbalanced.Rda")
}

@@

load("resultRatesImbalanced.Rda")
